%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  \cventry
  {Intern - Software Engineering} % Job title
  {Sysco LABS Technologies (Pvt) Ltd} % Organization
  {Sri Lanka} % Location
  {November 2023 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed Sysco Shop application that enables customers to order products online.}
      \item {Implemented Spring Boot and React JS layered architecture to ensure code reusability and maintainability.}
      \item {Developed applications with GraphQL and ElasticSearch.}
      \item {Created documentation that helps to understand the overall Search architecture in Sysco products suit.}
      \item {Developed high throuhput microservices with Spring Boot and Apache Kafka.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Software Engineer cum DevOps Engineer - Intern} % Job title
  {Imigap (PVT) Ltd} % Organization
  {Sri Lanka} % Location
  {May 2022 - May. 2023} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Orchestrated the deployment of live projects on AWS, ensuring smooth operation.}
      \item {Managed databases and servers, optimizing performance using AWS services.}
      \item {Implemented CI/CD pipelines on AWS to automate project workflows.}
      \item {Collaborated with senior engineers in code reviews to enhance code quality.}
      \item {Actively participated in Agile Scrum meetings and contributed to the code review process.}
    \end{cvitems}
  }

  \cventry
  {Business Analyst - Intern} % Job title
  {Commercial Technologies Plus} % Organization
  {Sri Lanka} % Location
  {Jul. 2022 - Dec. 2022} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed user interfaces (UI) for live projects using NEXT.JS, focusing on an intuitive user experience.}
      \item {Conducted comprehensive business analysis for live projects, identifying key requirements and objectives.}
      \item {Engaged with clients to gather project requirements, ensuring alignment with business goals.}
      \item {Created detailed documentation, including supporting evidence, to facilitate project understanding and execution.}
    \end{cvitems}
  }




  %---------------------------------------------------------
\end{cventries}
