%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  \cventry
  {Backend Developer and Scrum Master} % Affiliation/role
  {Be My Voice \href{https://github.com/kulasinghet/backend-be-voice}{\faGithubSquare}} % Project Name
  {UCSC} % Location
  {April 2023 - Nov. 2023} % Date(s)
  {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {Developed a cutting-edge mobile application that bridges communication gaps by translating Sinhala Sign Language to Sinhala Language, simultaneously serving as an educational tool for learning Sign Language.}
      \item {Implemented a privacy-centric approach by processing data locally on edge devices.}
      \item {Tech Stack: .NET Core, React Native, Azure, Docker, Kubernetes, Python, TensorFlow, OpenCV}
    \end{cvitems}
  }

  %---------------------------------------------------------
  %---------------------------------------------------------
  \cventry
  {Backend Developer and Scrum Master} % Affiliation/role
  {MedEx \href{https://github.com/kulasinghet/MedEx}{\faGithubSquare}} % Project Name
  {UCSC} % Location
  {Nov. 2022 - April 2023} % Date(s)
  {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {Spearheaded the development of MedEx, a web-based supply chain management system for the medical supplies sector.}
      \item {Applied Agile Software Development Methodology, adhering to Object-Oriented Design Principles, Design Patterns, and SOLID Principles.}
      \item {Tech Stack: PHP, MySQL, HTML, CSS, JavaScript}
    \end{cvitems}
  }

  %---------------------------------------------------------
  %---------------------------------------------------------
  \cventry
  {Backend Developer} % Affiliation/role
  {VisionVID - Co-Creator for Captivating Clips \href{https://github.com/kulasinghet/visionvid}{\faGithubSquare}} % Project Name
  {UCSC} % Location
  {2023} % Date(s)
  {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {AI powered Prompt to Video clip generator}
      \item {VisionVID can generate video according to the user prompt. Application harness the power of GPT3.5 Turbo and Learnado AI image genearator. }
      \item {Tech Stack: Express.js, React. FFMpeg, MongoDB}
    \end{cvitems}
  }


  \cventry
  {Backend Developer } % Affiliation/role
  {Unimate \href{https://github.com/kulasinghet/unimate}{\faGithubSquare}} % Project Name
  {UCSC} % Location
  {2023} % Date(s)
  {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {Engineered Unimate, a mobile application that secured victory at the MadHack Mobile Development Hackathon.}
      \item {Unimate is a mobile application that would help the universities to track student participation in a secure way}
      \item {Uses camera to scan QR codes to track student participation.}
      \item {Tech Stack: Flutter, Firebase}
      % \item {\href{http://www.resurchify.com}{Click Here}}
    \end{cvitems}
  }
  %---------------------------------------------------------
\end{cventries}
